A Fast kNN Algorithm Using Multiple Space-Filling Curves

### 2022-04-06 2022/Sensors/sensors.tex
fix typo in conclusion

The paper considers a classical machine learning method, the k nearest neighbour (kNN) method, which is widely used in machine learning practice and has been proven to perform very well because of its ``explainability'' (the decision to select an object class can be clearly explained). The results of practical implementation of one of kNN acceleration approaches based on dimensionality reduction using space-filling curves are presented.

>>>>

The paper considers a classical machine learning method, the k nearest neighbour (kNN) method, which is widely used in machine learning practice and has been proven to perform very well because of its ``explainability'' (the decision  regarding the choice of an object class can be clearly explained). The results of practical implementation of one of kNN acceleration approaches based on dimensionality reduction using space-filling curves are presented.
